\section{Basic functions}
\funcSignature{(++) :: [a] \rightarrow [a] \rightarrow [a]}
Append two lists, i.e.,
\begin{align*}
	&[x1, ..., xm] ++ [y1, ..., yn] == [x1, ..., xm, y1, ..., yn]\\
	&[x1, ..., xm] ++ [y1, ...] == [x1, ..., xm, y1, ...]
\end{align*}
If the first list is not finite, the result is the first list.

\funcSignature{head :: [a] \rightarrow a }
Extract the first element of a list, which must be non-empty.

\funcSignature{last :: [a] \rightarrow a }
Extract the last element of a list, which must be finite and non-empty.

\funcSignature{tail :: [a] \rightarrow [a] }
Extract the elements after the head of a list, which must be non-empty.

\funcSignature{init :: [a] \rightarrow [a] }
Return all the elements of a list except the last one. The list must be non-empty.
\skipped

\funcSignature{uncons :: [a] \rightarrow Maybe (a, [a]) }
Decompose a list into its head and tail. If the list is empty, returns Nothing. If the list is non-empty, returns Just (x, xs), where x is the head of the list and xs its tail.
Since: 4.8.0.0

\funcSignature{null :: Foldable\; t \Rightarrow t\; a \rightarrow Bool}
Test whether the structure is empty. The default implementation is optimized for structures that are similar to cons-lists, because there is no general way to do better.

\funcSignature{length :: Foldable\; t \Rightarrow t\; a \rightarrow Int}
Returns the size/length of a finite structure as an Int. The default implementation is optimized for structures that are similar to cons-lists, because there is no general way to do better.